---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tidydrc

<!-- badges: start -->

<!-- badges: end -->

The goal of {tidydrc} is to create a programmatic, 'tidy' interface to the {drc} package for fitting various dose-response models to large amounts of experimental data.

This package leverages the `tidyr::nest()` and `purrr::map()` workflow for keeping raw data, fitted models, predictions, and relevant model coefficients together in a single data frame.

> This is a fork and refactor of the original [{tidydrc}](<https://github.com/angelovangel/tidydrc>) that had a stalled development. Credit for original creation goes to Angel Angelov.

## Installation

<!-- You can install the released version of {tidydrc} from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->

<!-- install.packages("tidydrc") -->

<!-- ``` -->

Install the development version:

```{r, eval=FALSE}
devtools::install_github("bradyajohnston/tidydrc")
```

## Example

With a single function, we fit a `LL.4()` 4 parameter log-logistic dose-response model do the example data `S.alba`.

```{r}
library(tidydrc)
```

```{r}
str(S.alba)
```

`S.alba` is data from two Herbicide treatments, and contains Dose info as well as the ,response to the Dose (`DryMatter`),

Into the `tidydrc_mode()` function we supply the data frame, dose and response columns, the model we wish to fit (defaults to `LL.4()`) and and columns we wish to group by -- in this case the Herbicide treatment.

```{r example}
fitted <- tidydrc_model(
	data = S.alba, 
	dose = Dose, 
	response = DryMatter, 
	model = LL.4(), 
	Herbicide
	)

fitted
```

The result of the `tidydrc_model()` function is a `tibble` that has a row for each group. Each column is a nested object. Associated with each group we have the `data`, the fitted `drmod` model, the model residuals `resid`, the fitted curve data in `pred` and the coefficients from the model in `coefs`.

The user can use `tidyr::unnest()` to access relevant information and create plots and tables for reporting. The convenience function `tidydrc_plot()` is provided for quickly plotting the results. The result can then me modified like any other {ggplot2} plot such as `ggplot2::facet_wrap()` .

```{r plot-example}
fitted %>% 
	tidydrc_plot(
		ed50 = FALSE, 
		confint = FALSE, 
		colour = ~Herbicide
	) + 
	ggplot2::facet_wrap(~Herbicide) + 
	ggplot2::theme(legend.position = "")
```
